Iterative Monomorphisation

### 2024-06-26 iterative_monomorphisation.tex
a couple new numbers

\begin{table}[ht]
\caption{Evaluation of native polymorphism vs.\ monomorphisation}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & Native & Mono & Union \\
   \midrule
   E  &   & 0 & 0 \\
   Leo-III & 157 with E & 0 & 0 \\ % Leo-III's performance is comparatively very poor, not coherent with casc results
   Leo-III &  with cvc4 & 0 & 0 \\ % Leo-III's performance is comparatively very poor, not coherent with casc results
   Satallax &  & 0 & 0 \\
   Vampire & 0 & 0 & 0 \\ % Vampire's parser fails on too many polymorphic problems (about 1/3 of them)
   Zipperposition & 335 & 0 & 0 \\[1.5\jot]
   Total & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\caption{Evaluation of native polymorphism vs.\ monomorphisation}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & Native & Mono & Union \\
   \midrule
   E  &   & 0 & 0 \\
   Leo-III &  157 with E & 0 & 0 \\ 
   Leo-III &  68 with cvc4 & 0 & 0 \\ % same as without anything for the native case
   Satallax &  & 0 & 0 \\
   %Vampire & 0 & 0 & 0 \\ % Vampire's parser fails on too many polymorphic problems (about 1/3 of them)
   Zipperposition & 339 & 0 & 0 \\[1.5\jot]
   Total & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}
